---
title: "Explore different happy moments for single men and women"
author: "Lei Bao"
output: html_notebook
runtime: shiny
---
Here, we explore this data set and try to answer the question, "How different is it to make single men and women happy?"


```{r load libraries, warning=FALSE, message=FALSE}
library(dplyr)
library(shiny)
```


```{r}
demographic <- read.csv("../data/demographic.csv")
cleaned_hm <- read.csv("../data/cleaned_hm.csv")
```

### Merge the datasets based on 'wid', Filter for single males and females, Select relevant columns (assuming all from cleaned_hm and only necessary from demographic), Write the final data to a new CSV file
```{r}

merged_data <- merge(cleaned_hm, demographic, by = "wid")

single_data <- filter(merged_data, marital == "single" & (gender == "m" | gender == "f"))

final_data <- select(single_data, names(cleaned_hm), age, country, gender)

write.csv(final_data, "../output/single_happy_moments.csv", row.names = FALSE)

```

###Split the data into two separate data frames based on gender
```{r}
single_data <- read.csv("../output/single_happy_moments.csv")
single_males <- subset(single_data, gender == "m")
single_females <- subset(single_data, gender == "f")
write.csv(single_males, "../data/single_males.csv", row.names = FALSE)
write.csv(single_females, "../data/single_females.csv", row.names = FALSE)
```


```{r}


# Define UI
ui <- fluidPage(
  titlePanel("Analysis of Single Males and Females Happiness Data"),
  
  sidebarLayout(
    sidebarPanel(
      selectInput("gender", "Choose Gender:",
                  choices = c("Male", "Female")),
      downloadButton("downloadData", "Download CSV")
    ),
    
    mainPanel(
      tableOutput("viewData")
    )
  )
)

# Define server logic
server <- function(input, output) {
  
  # Reactive expression to read the selected dataset
  datasetInput <- reactive({
    switch(input$gender,
           "Male" = read.csv("../data/single_males.csv"),
           "Female" = read.csv("../data//single_females.csv"))
  })
  
  # Render the table in the UI
  output$viewData <- renderTable({
    datasetInput()
  })
  
  # Downloadable csv of selected dataset
  output$downloadData <- downloadHandler(
    filename = function() {
      paste(input$gender, "data.csv", sep = "_")
    },
    content = function(file) {
      write.csv(datasetInput(), file, row.names = FALSE)
    }
  )
}

# Run the application 
shinyApp(ui = ui, server = server)


```
###This 







